# Code

```{r eval=TRUE,echo=TRUE,results='hold'}
# US Populated Places

# https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-06-27

# html output : https://saecanet.com/tidytuesday-2023-06-27-US-Populated-Places.html

# Loading packages

# library(tidylog)
library(tidyverse)
rstudioapi::getSourceEditorContext()$path %>% dirname() %>% setwd()

# Loading source data
us_place_names <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-06-27/us_place_names.csv')
us_place_history <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-06-27/us_place_history.csv')
```

## Glimpse

```{r eval=TRUE,echo=TRUE,results='hold'}
glimpse(us_place_names)
```

```{r eval=TRUE,echo=TRUE,results='hold'}
glimpse(us_place_history)
```

## Check original data

```{r eval=FALSE,echo=TRUE,results='hold'}
options(timeout = 120)
url <- "https://prd-tnm.s3.amazonaws.com/StagedProducts/GeographicNames/DomesticNames/DomesticNames_National_Text.zip"
destfile <- url %>% gsub('^.+/([^/]+$)','\\1',.)
setwd('D:/tidytuesday/')
download.file(url = url,destfile = destfile)
(buf0 <- unzip(destfile))
df0 <-  read_delim(buf0[1], "|")
write.csv(x = df0,file = 'DomesticNames_National_Text.csv',quote = T,na = '',fileEncoding = 'UTF-8',row.names = F)
```

```{r eval=TRUE,echo=TRUE,results='hold'}
setwd('D:/tidytuesday/')
df <- read.csv(file = 'DomesticNames_National_Text.csv',check.names = F)
df$feature_class %>% unique()
```

## Check description

```{r eval=TRUE,echo=TRUE,results='hold'}
library(rvest)
(df_description <- 
  'https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-06-27' %>% read_html()  %>% html_table())
```

## Display descriptions

```{r eval=TRUE,echo=TRUE,results='asis'}
df_description[[1]] %>% DT::datatable(options = list(lengthMenu = list(c(10, -1),c("10","All"))))
```

```{r eval=TRUE,echo=TRUE,results='asis'}
df_description[[2]] %>% DT::datatable(options = list(lengthMenu = list(c(10, -1),c("10","All"))))
```

## Check NA

```{r eval=TRUE,echo=TRUE,results='hold'}
us_place_names %>% apply(MARGIN = 2,FUN = function(x)sum(is.na(x))) %>% data.frame()
```

```{r eval=TRUE,echo=TRUE,results='hold'}
us_place_history %>% apply(MARGIN = 2,FUN = function(x)sum(is.na(x))) %>% data.frame()
```

## Description of feature class

```{r eval=TRUE,echo=TRUE,results='hold'}
'https://www.usgs.gov/us-board-on-geographic-names/gnis-domestic-names-feature-classes' %>% read_html() %>% html_nodes('table.usa-table--striped') %>% html_table(header = T) %>% data.frame() %>% DT::datatable(options = list(lengthMenu = list(c(10, -1),c("10","All"))))
```

- **Populated Place**:Place or area with clustered or scattered buildings and a permanent human population (city,settlement, town, village). A populated place is usually not incorporated and by definition has no legal boundaries. However, a populated place may have a corresponding "civil" record,the legal boundaries of which may or may not coincide with the perceived populated place.Distinct from Census and Civil classes.
- Source:https://www.usgs.gov/us-board-on-geographic-names/gnis-domestic-names-feature-classes

## Plot

```{r eval=TRUE,echo=TRUE,results='hold'}
# Check for communities that have been entered into the system more than once.
df <- us_place_names
df <- (!is.na(df$prim_lat_dec) & !is.na(df$prim_long_dec) & !is.na(df$date_created)) %>% df[.,]
glimpse(df)
df$forcheckduplicated <- paste0(df$prim_lat_dec,df$prim_long_dec,df$state_name,df$county_name)
```

```{r eval=TRUE,echo=TRUE,results='hold'}
# example 1
example <- df$forcheckduplicated %>% duplicated() %>% which() %>% tail(1)
(df$forcheckduplicated[example]==df$forcheckduplicated) %>% df[.,]
```

```{r eval=TRUE,echo=TRUE,results='hold'}
# example 2
example <- df$forcheckduplicated %>% duplicated() %>% which() %>% tail(2) %>% head(1)
(df$forcheckduplicated[example]==df$forcheckduplicated) %>% df[.,]
```

```{r eval=TRUE,echo=TRUE,results='hold'}
df$year <- df$date_created %>% year()
df$year %>% table() %>% data.frame()
```

```{r eval=TRUE,echo=TRUE,results='hold'}
AllCounty <- map_data("county")
MainStates <- map_data("state")
xrange <- MainStates$long %>% range()
yrange <- MainStates$lat %>% range()
g0 <- 
  ggplot() + 
  geom_polygon(data = AllCounty,
               mapping = aes(x = long,y = lat,group = group),
               color = "darkblue", 
               fill = "white",
               linewidth = .1 ) +
  geom_polygon(data = MainStates,
               mapping = aes(x = long,y = lat,group = group),
               color = "black",
               fill = "white",
               linewidth = 1,
               alpha = .3) + 
  theme_minimal()
```

```{r eval=TRUE,echo=TRUE,results='hold'}
df$year %>% unique() %>% sort()
```

```{r eval=TRUE,echo=TRUE,results='hold'}
era_s <- df$year %>% range() %>% {seq(.[1],.[2],by = 13)}
era_e <- tail(era_s-1,-1) %>% c(.,max(df$year))
df$era <- 
  df$year %>% 
  {ifelse(test = era_s[1]<=. & .<=era_e[1],
          yes = paste0(era_s[1],'-',era_e[1]),
          no = ifelse(test = era_s[2]<=. & .<=era_e[2],
                      yes = paste0(era_s[2],'-',era_e[2]),
                      no = ifelse(test = era_s[3]<=. & .<=era_e[3],
                                  yes = paste0(era_s[3],'-',era_e[3]),
                                  no = paste0(era_s[4],'-',era_e[4]))))}
g <- 
  g0 + geom_point(mapping = aes(x = prim_long_dec,y = prim_lat_dec),
                 data = df,
                 size = 1,
                 col = 'red') + 
  ylim(yrange) + 
  facet_wrap(facets = . ~ era,nrow = 2) + 
  theme(axis.title = element_blank(),
        axis.text = element_text(size = 15),
        strip.text = element_text(size = 16),
        plot.title = element_text(hjust = 0.5,size = 17)) + 
  labs(title = 'The community location entered into GNIS with the class name "Populated Place".(U.S. mainland only)') + 
  coord_fixed() + 
  scale_x_continuous(breaks = scales::pretty_breaks(10),limits = xrange)
```

```{r eval=TRUE,echo=TRUE,results='hide'}
# Chart output
setwd('D:/tidytuesday/');getwd()
png(paste0("tidytuesday-2023-06-27-US-Populated-Places.png"),width = 1000,height = 600)
g %>% print()
dev.off()

# ALT

## Chart type : Four scatterplots drawn on a map of the U.S. mainland.

## Type of data : Location of communities entered as "Populated Place" in the GNIS for each of the four age groups.

## Reason for including the chart : To see the chronological evolution of the location and number of communities entered as "Populated Place" in GNIS.

## Link to data or source : https://github.com/rfordatascience/tidytuesday/tree/master/data/2023/2023-06-27
```

# `r referencetxt`

- https://remiller1450.github.io/s230s19/Intro_maps.html
- https://edits.nationalmap.gov/apps/gaz-domestic/public/search/names
- https://www.usgs.gov/us-board-on-geographic-names/gnis-domestic-names-feature-classes
